---
title: "Analysis - CM Prolific"
author: "Aaron"
date: "October 03, 2019"
output: rmarkdown::github_document
---

Analysis of data collected from Cleveland McGill replication experiment run on Prolific

References:  
 - https://github.com/mjskay/tidybayes  
 - @codementum  

## Grab the json file and convert into a list in R
```{r}
library("jsonlite")
library(RCurl)

tables <- read_json("https://clevelandmcgill-c116c.firebaseio.com/.json", simplifyVector = TRUE)
# str(tables)
```

```{r}
tables$Session
```

## Create the session tibble
```{r}
library(tidyverse)

sessions <- tibble()
for (session in tables$Session) {
  new_row <- as_tibble(session)
  sessions <- sessions %>% bind_rows(new_row)
}
sessions
```

## Create the trials tibble
```{r}
trials = tibble()
for (img_name in tables$Trials) {
  for (observation in img_name) {
      new_row <- as_tibble(observation)
      trials <- trials %>% bind_rows(new_row)
    # trials <- rbind(trials_df, data.frame(observation))
  }
}
trials
```

## Create `condition` column from `image_name`
```{r}
trials$condition <- NA
for (i in seq_along(trials$image_name)) {
  if (substr(trials$image_name[i], 3, 3) == 'B')
    condition <- 'Bar'
  else if (substr(trials$image_name[i], 3, 3) == 'P')
    condition <- 'Pie'
  else
    condition <- '???'
  
  trials$condition[i] <- condition
}

trials
```

## Create column for absolute response error
```{r}
trials$abs_difference <- NA
for (i in seq_along(trials$actual_answer)) {
  trials$abs_difference[i] <- abs(strtoi(trials$actual_answer[i]) - strtoi(trials$expected_answer[i]))
}

trials
```

## TODO: Create `participant` column from `session_id` (session_id looks ugly in facet plot)
```{r}
unique(trials$session_id)
```

## Comparing Bar and Pie performance
```{r}
trials %>%
  ggplot(aes(x = condition, y = abs_difference)) +
  geom_point(alpha = 0.5) +
  stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 1.0, alpha=0.5) +
  coord_flip()
```

## Comparing individual participant performance
```{r}
trials %>%
  ggplot(aes(x = condition, y = abs_difference)) +
  geom_point(alpha = 0.5) +
  stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 1.0, alpha=0.5) +
  facet_wrap(~ session_id)

ggsave('barvpie_byparticipant.pdf', units="in", width=5, height=8)
```

## TODO: t-tests to compare Bar and Pie performance

```{r}

```

